\documentclass[a4paper, 11pt]{proc}
\begin{document}
\title{Fashion Show - Advika}
\author{Rule Book}
\maketitle

\section*{Description}
This will be a competition between both designers and models. It aims to challeng one's creativity by compelling one to present funky combination with both aethetics adn uniqueness(advika).
\section*{Rules}
\begin{enumerate}
	\item All the Int. MSc. and PhD. students can participate in the event.
	\item Each contestant will register individually.
	\item First rounds for both male and female will consist of ramp walk, posing and a 1 min to 3 min speech about them and their costumes. Each candidate will be given a maximum of 4 min for this round.
	\item Round 1 is an elimination round.
	\item Contestants who reach round 2 will be paired up with other contestant based on chit system.
	\item In Round 2 contestants have to do a pair ramp walk with their designated partners and pose as a pair. The pair can have multiple poses.
	\item In round 2 contestants will be judged by individually based on how the pair showcases their chemistry and their ability to capture the moment in photos.
	\item The order of appearance will be determined by chit system.
	\item The contestants will be scored by the judges based on their Confidence, Costume, Walking Style, and the Speech. In both the rounds the contestants will be judges individually.
	\item The decision of the judges shall be final and binding to all.
	\item Contestants are required to bring their own Props, Costumes and Make-up. None will be provided by the organizers.
	\item Contestants will be provided with rooms before rounds for preparation.
	\item Organisers are not responsible for the insurance of the contestants.
	\item Will be 2 prizes:- winner(male) and winner(female).
	\item If there are less than 5 contestants in any category, then the categories will be merged.
	\item The contestants can take help from other non-participating students of NISER for preparing their costumes. In such cases, it is contestant's responsibility to mention their names if they are awarded.
	\item Theme for the event: Fusion of Indian-regional dress with other dress from foreign countries.Ex:You can fuse Chinese or Japanese attire with a north-east Indian.
	\item The organising committee reserves the right to make changes to these rules.
\end{enumerate}
The Judges are Akhil Ranjan, software engineer and photographer and Ankita Mishra, Law professional and Actor.

Event Coordinators:- Dhairya Patel and Abhishek Anil Deshmukh

For Queries about the theme contact: Payal Priyadarsani-7788809128, Vaishnavi Awasthi-9827466135
\end{document}
